What do incoming university students believe about open science practices in

### 2021-03-09 analysis/Manuscript.Rmd
One para amended slightly

#I've commented this paragraph out because on reflection I'm not sure it's a very strong argument, and the potential effect of teaching about replicability on levels of trust in psych science isn't really something we can directly address in this study.
However, it was one of the only places where we really talked about the Chopik et al. 2018 paper, which probably needs more coverage.

@@

<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch?
9Mar: On reflection I think it's kinda an ok argument, albeit we need more evidence for the claims in it. 
I almost want to phrase it as saying that "Undergraduate students are both our most important customers and our most important suppliers of data"...
-Matt
-->

These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students know and believe about these topics already. Currently, relatively little is know about undergraduate students' beliefs about replicability and open science practices. A study of by @chopikHowWhetherTeach2018 (focused on the effect of a one-hour lecture about open science) found that students tended to endorse pro-replicability/open science beliefs after the lecture (e.g., 92.7% thought it was "very" or "extremely" important that researchers "make data publicly available so that results can be verified by other researchers"). However, this study was obviously not

>>>>

#I've commented this paragraph out because on reflection I'm not sure it's a very strong argument, and the potential effect of teaching about replicability on levels of trust in psych science isn't really something we can directly address in this study.

@@

These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students know and believe about these topics already. Currently, relatively little is know about undergraduate students' beliefs about replicability and open science practices. A study of by @chopikHowWhetherTeach2018 (focused on the effect of a one-hour lecture about open science) found that students tended to endorse pro-replicability/open science beliefs after the lecture (e.g., 92.7% thought it was "very" or "extremely" important that researchers "make data publicly available so that results can be verified by other researchers"). However, this study was aimed primarily at estimating the effect of the lecture rather than describing students knowledge and beliefs per se. @bottesiniParticipantsCareIf2019 plan a registered report focusing on participants' (including undergraduate students') attitudes to p-hacking, but the final report has not yet been published. In sum, little is currently known about undergraduate psychology students' beliefs about replicability and open science.
